MG7: Configurable and scalable 16S metagenomics data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
remove equal contribution remark

\author[1]{Alexey Alekhin\(^\dagger\)} \affil[1]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[2]{Evdokim Kovach\(^\dagger\)} \affil[2]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[3]{Marina Manrique} \affil[3]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[4]{Pablo Pareja-Tobes} \affil[4]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[5]{Eduardo Pareja} \affil[5]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[6]{Raquel Tobes} \affil[6]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[7]{Eduardo Pareja-Tobes} \affil[7]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}

@@

\begin{abstract}
As part of the Cambrian explosion of omics data, metagenomics brings to
the table a specific, defining trait: its social essence. The
\emph{meta} prefix exerts its influence, with multitudes manifesting
themselves everywhere; from samples to data analysis, from actors
involved to (present and future) applications. Of these dimensions, data
analysis is where needs lay further from what current tools provide. Key
features are, among others, scalability, reproducibility, data
provenance and distribution, process identity and versioning. These are
the goals guiding our work in MG7, a 16S metagenomics data analysis
system. The basic principle is a new approach to data analysis, where
configuration, processes, or data locations are static, type-checked and
subject to the standard evolution of a well-maintained software project.
Cloud computing, in its Amazon Web Services incarnation, when coupled
with these ideas, produces a robust, safely configurable, scalable tool.
Processes, data, machine behaviors and their dependencies are expressed
using a set of libraries which bring as much as possible checking and
validation to the type level, without sacrificing expressiveness.
Together they form a toolkit for defining scalable cloud-based workflows
composed of stateless computations, with a static reproducible
specification of dependencies, behavior and wiring of all steps. The
modeling of taxonomy data is done using Bio4j, where the new paradigm of
graph databases allows for both a simple expression of taxonomic
assignment tasks and the calculation of taxa abundance values
considering the hierarchic structure of the taxonomy tree. MG7 includes
a new 16S reference database, \emph{16S-DB7}, built with a flexible and
sustainable update system, and the possibility of project-driven
personalization. \(^\dagger\) The first and second authors contributed
equally to this work.
\end{abstract}

@@

\bibliography{./out/../refs}

>>>>

\author[1]{Alexey Alekhin} \affil[1]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[2]{Evdokim Kovach} \affil[2]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[3]{Marina Manrique} \affil[3]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[4]{Pablo Pareja-Tobes} \affil[4]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[5]{Eduardo Pareja} \affil[5]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[6]{Raquel Tobes} \affil[6]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}
\author[7]{Eduardo Pareja-Tobes} \affil[7]{\emph{\href{http://ohnosequences.com}{oh no sequences!}} research group,
\href{http://www.era7bioinformatics.com}{Era7 bioinformatics}}

@@

\begin{abstract}
As part of the Cambrian explosion of omics data, metagenomics brings to
the table a specific, defining trait: its social essence. The
\emph{meta} prefix exerts its influence, with multitudes manifesting
themselves everywhere; from samples to data analysis, from actors
involved to (present and future) applications. Of these dimensions, data
analysis is where needs lay further from what current tools provide. Key
features are, among others, scalability, reproducibility, data
provenance and distribution, process identity and versioning. These are
the goals guiding our work in MG7, a 16S metagenomics data analysis
system. The basic principle is a new approach to data analysis, where
configuration, processes, or data locations are static, type-checked and
subject to the standard evolution of a well-maintained software project.
Cloud computing, in its Amazon Web Services incarnation, when coupled
with these ideas, produces a robust, safely configurable, scalable tool.
Processes, data, machine behaviors and their dependencies are expressed
using a set of libraries which bring as much as possible checking and
validation to the type level, without sacrificing expressiveness.
Together they form a toolkit for defining scalable cloud-based workflows
composed of stateless computations, with a static reproducible
specification of dependencies, behavior and wiring of all steps. The
modeling of taxonomy data is done using Bio4j, where the new paradigm of
graph databases allows for both a simple expression of taxonomic
assignment tasks and the calculation of taxa abundance values
considering the hierarchic structure of the taxonomy tree. MG7 includes
a new 16S reference database, \emph{16S-DB7}, built with a flexible and
sustainable update system, and the possibility of project-driven
personalization.
\end{abstract}

@@

\bibliography{out/../refs}
